\textls[-0]{\thetitle}

### 2023-03-21 stlc-linkage-typing-named.tex
Done Changing to named variables.
Fix B in Wsig
W-types
bugfix in STLC encoding figure
tweaks to avoid margin overrun

\goodTerm{\TyTkg{\lsig_0}}{\seal_1}{\sub{

@@

}{\SubstWeak{1}}}

@@

$\quad \{\wsig_{\texttt{tm}}^0 \coloneq \WSigAdd{\WSigEmp}{\bbone}{\bbzero},
 \ \  \wsig_{\texttt{tm}}^1 \coloneq \WSigAdd{\wsig_{\texttt{tm}}^0}{\bbone}{\bbtwo}\ \ ...,  \wsig_{\texttt{tm}}\}$

@@

\goodTerm{\TyTkg{\lsig_1}}{\seal_2}{\sub{

@@

\goodTerm{\TyTkg{\lsig_5}}{\seal_6}{\sub{

@@

}{\SubstWeak{1}}}

@@

    \tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T6-b}(-0.02,-0.10)(-0.02,0.28)
    \CaseSig{\top}{\bot}{
        \fontsize{8.5}{10.2}\selectfont
        \text{$\El{\mathit{self}.\texttt{tm}}\to\mathit{id}\to\El{\mathit{self}.\texttt{tm}}$}

@@

\goodTerm{\TyTkg{\lsig_9}}{\seal_{10}}{\sub{

@@

    \begin{minipage}{.20\textwidth}%

@@

    \tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T10-b}(-0.02,-0.26)(-0.02,0.40)

@@

        \El{\mathit{self}.\texttt{tm}} \to \El{\mathit{self}.\texttt{tm}}

@@

        \to \mathit{id} \to \El{\mathit{self}.\texttt{tm}}

>>>>

\goodTerm{x : \TyTkg{\lsig_0}}{\seal_1}{{

@@

}{}}

@@

@@

\goodTerm{x : \TyTkg{\lsig_1}}{\seal_2}{{

@@

\goodTerm{x : \TyTkg{\lsig_5}}{\seal_6}{{

@@

}}

@@

    \tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T6-b}(-0.05,-0.30)(-0.02,0.46)
%   \CaseSig{\top}{\bot}{
    \texttt{CaseTy}\left(\top,\bot,
        \begin{minipage}{.15\textwidth}%
            \El{\mathit{self}.\texttt{tm}} \to
            \mathit{id} \to \El{\mathit{self}.\texttt{tm}}
    \right)
%   }

@@

\goodTerm{x : \TyTkg{\lsig_9}}{\seal_{10}}{{

@@

    \begin{minipage}{.15\textwidth}%

@@

    \tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T10-b}(-0.02,-0.45)(-0.02,0.60)

@@

        \El{\mathit{self}.\texttt{tm}} \to

@@

        \El{\mathit{self}.\texttt{tm}} \to
        \mathit{id} \to \El{\mathit{self}.\texttt{tm}}
